% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Milosz Kowal}
\newcommand{\CVTitle}{Milosz Kowal Resume}
\newcommand{\CVNote}{Resume compiled on {\today}}
\newcommand{\CVWebpage}{https://miloszkowal.com}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
\begin{comment}
\end{comment}
\href{mailto:milosz.j.kowal@gmail.com}
{milosz.j.kowal@gmail.com}
\,\SubBulletSymbol\,
+1\,(630)\,447-0764
\,\SubBulletSymbol\,
\href{\CVWebpage}
{miloszkowal.com}
\end{subtitle}

\begin{body}


%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\section
{Professional\newline References}
{References}
{PDF:References}

{\textbf{Pavan Srivastava}}
\hfill
\GapNoBreak
\BulletItem
Associate Vice President, Software Engineering, Moody's Corporation
\BulletItem
Email: \href{mailto:pavan.srivastava@moodys.com}{pavan.srivastava@moodys.com}
\BulletItem
Mr. Srivastava was my supervisor on the CMS Product Team at Moody's. He is intimately familiar with the projects I am involved in and can speak to my technical proficiency, particularly with natural language processing in Python and automation testing using PyTest and Jenkins.

\BigGapNoBreak

{\textbf{Sophie H. Howard}}
\hfill
\GapNoBreak
\BulletItem
Assistant Director of Admissions, Office of Enrollment and Student Success, Trinity College
\BulletItem
Email: \href{mailto:sophie.howard@trincoll.edu}{sophie.howard@trincoll.edu}
\BulletItem
Phone: (860) 297-2180
\BulletItem
Ms. Howard was my direct supervisor in the Office of Enrollment and Student Success. She can speak to my public speaking skills, my writing, and evaluative abilities.

\BigGapNoBreak

{\textbf{Angel B. Pérez, Ph.D.}}
\hfill
\GapNoBreak
\BulletItem
Vice President for Enrollment and Student Success, Trinity College
\BulletItem
Email: \href{mailto:angel.perez@trincoll.edu}{angel.perez@trincoll.edu}
\BulletItem
Phone: (860) 297-2175
\BulletItem
Dr. Pérez served as my supervisor in the Office of Enrollment and Student Success. He can speak to my conscientiousness, my work ethic, and my interpersonal skills.

\BigGapNoBreak

{\textbf{Professor Per Sebastian Skardal, Ph.D.}}
\hfill
\GapNoBreak
\BulletItem
Assistant Professor, Department of Mathematics, Trinity College
\BulletItem
Email: \href{mailto:persebastian.skardal@trincoll.edu}{persebastian.skardal@trincoll.edu}
\BulletItem
Phone: (860) 297-2299
\BulletItem
Professor Skardal and I conducted an independent study in dynamical systems and chaos theory. He can speak to my analytic abilities and my experience with Matlab.

\BigGapNoBreak

{\textbf{Sarah Lucas}}
\hfill
\GapNoBreak
\BulletItem
Assistant Director, Office of Student Activities, Involvement \& Leadership, Trinity College
\BulletItem
Email: \href{mailto:sarah.lucas@trincoll.edu}{sarah.lucas@trincoll.edu}
\BulletItem
Phone: (860) 297-4187
\BulletItem
Ms. Lucas and I have worked on establishing and developing the Trinity College Student Photographers from a fledgling club to a bustling student-run organization. She can speak to my management and leadership skills.


\begin{comment}
\noindent\hrulefill
\section
{Personal\newline References}
{References}
{PDF:References}

{\textbf{Christopher Reader}}
\hfill
\GapNoBreak
\BulletItem
Self-Employed Photographer
\BulletItem
Email: \href{mailto:hopelessdfilms@gmail.com}{hopelessdfilms@gmail.com}
\BulletItem
Phone: (630) 333-3797
\BulletItem
Mr. Reader has served as a mentor and photography coach for many years. He and I have worked at the Illinois Mathematics and Science Academy together to expand access to multimedia resources for all students. He can speak to my entrepreneurial drive and my technology skills.
\end{comment}
\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\begin{flushright}
\UseNoteFont
%[\textit{\CVNote}]
\hspace{2.0mm}\null
\end{flushright}
%\label{LastPage}
\end{document}
