% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Milosz Kowal}
\newcommand{\CVTitle}{Milosz Kowal Resume}
\newcommand{\CVNote}{Resume compiled on {\today}}
\newcommand{\CVWebpage}{https://miloszkowal.com}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
%\href{https://goo.gl/maps/nvgKtniZiYF2}
%{558A Kingston Ave, Apt 4A, Brooklyn, NY 11203}
\par
\href{mailto:me@miloszkowal.com}
{me@miloszkowal.com}
\,\SubBulletSymbol\,
+1\,(630)\,447-0764
\,\SubBulletSymbol\,
\href{\CVWebpage}
{miloszkowal.com}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

Programming: Python, R, PHP, mySQL, HTML5, CSS3, PostgreSQL, Matlab, Mathematica, Git, \LaTeX \hfill\break
Certifications: Bloomberg Market Concepts, Google Analytics


%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\noindent\hrulefill
\section
{Education}
{Education}
{PDF:Education}

\href{http://www.trincoll.edu}
{\textbf{Trinity College}},
Hartford, Connecticut
\hfill
\DatestampYMD{2014}{08}{01} --
\DatestampYMD{2018}{05}{20}

\GapNoBreak
\BulletItem
Bachelor of Science (B.S.) in
Mathematics and Theater, GPA: 3.7/4.0
\begin{detail}
\SubBulletItem
Coursework: Linear Algebra, Abstract Algebra, Analysis, Differential Equations, Chaos Theory
\SubBulletItem
Honors and Awards: \textit{cum laude}, Pi Mu Epsilon Inductee (Spring 2018)
\end{detail}

\GapNoBreak
\href{http://www.imsa.edu}
{\textbf{Illinois Mathematics and Science Academy}},
Aurora, Illinois
\hfill
\DatestampYMD{2011}{09}{01} --
\DatestampYMD{2014}{05}{01}
\GapNoBreak
\BulletItem
Attended second-highest rated public high school in the United States.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent\hrulefill
\section
{Selected\newline
Experience}
{Other Work Experience}
{PDF:WorkExperience}

\href{http://www.moodys.com}
{\textbf{Moody's Corporation}},
New York City, New York
\hfill
\DatestampYMD{2018}{07}{30} --
\DatestampYMD{2019}{07}{29}

\GapNoBreak
\BulletItem
Software Engineer
\begin{detail}
\SubBulletItem
Implemented and maintained four APIs in Python, providing machine learning services in fuzzy matching, content summarization, thematic tagging, and written content review. Was deployed into production with over 2,000 research writers.
\SubBulletItem
Implemented an automated test library for above APIs using PyTest and Jenkins, eliminating the need for manual qualitative testing. Reports were generated in Allure.
\SubBulletItem
Designed high-level logic and process flow for caching and storing machine-generated text content, reducing retrieval time from $\mathnormal{O(n)}$ time to $\mathnormal{O(1)}$ time.
\end{detail}

\begin{comment}
\BigGapNoBreak
{\textbf{Trinity College Office of Enrollment}},
Hartford, Connecticut
\hfill
\DatestampYMD{2017}{08}{21} --
\DatestampYMD{2018}{05}{18}


\GapNoBreak
\BulletItem
Student Admissions Associate
\begin{detail}
\SubBulletItem
Conducted interviews with over 50 high school students, evaluating their standing as applicants, which resulted in 11 admitted students for the Class of 2022.
\SubBulletItem
Submitted written evaluations on each applicant to be added to applicant’s file.
\SubBulletItem
Led weekly group information sessions for prospective students, families, and admissions visitors.
\SubBulletItem
Participated in on-campus recruitment events, such as panels, special programs, and other projects.
\end{detail}
\end{comment}

\BigGapNoBreak
\href{http://www.trincoll.edu}
{\textbf{Trinity College Information Technology Services}},
Hartford, Connecticut
\hfill
\DatestampYMD{2014}{09}{15} --
\DatestampYMD{2018}{05}{11}

\GapNoBreak
\BulletItem
Head Solutions Engineer
\begin{detail}
\SubBulletItem
Trained and evaluated over 15 new employees, analyzing performance trends using Crystal Reports.
\SubBulletItem
Provided support on over 4,900 service requests, logging all details in SolarWinds Web Helpdesk.
\SubBulletItem
Drafted Bash script to automate process within network infrastructure, resulting in substantial decreases in service requests related to that issue.
\SubBulletItem
Cooperated with architectural design team to create new solutions for user body of over 2,200 students, faculty, and staff.
\end{detail}

\BigGapNoBreak
{\textbf{Navier, Inc.}},
Chicago, Illinois
\hfill
\DatestampYMD{2012}{06}{15} --
\DatestampYMD{2013}{12}{01}

\GapNoBreak
\BulletItem
Chief UI/UX Design Engineer
\begin{detail}
\SubBulletItem
Created platform enabling web developers to interact with consumers to improve prototype versions of apps.
\SubBulletItem
Leveraged AngularJS, CSS3, and HTML5 in constructing front-end interface for customer-facing products.
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%
%% SELECTED PROJECTS %%
%%%%%%%%%%%%%%%%%%%%%%%

\noindent\hrulefill
\section
{Selected Projects}
{Selected Projects}
{PDF:Selected Projects}

\href{https://github.com/miloszkowal/PyMessage}
{\textbf{PyMessage}} | NLTK, Pandas, SQLite, Tableau
\hfill

\GapNoBreak
Python and NLTK library for sentiment analysis of arbitrary strings of characters, pulled from over 200K text messages stored in a SQLite database locally on macOS. Publishes results in CSV format for ingestion into Tableau and other visualization programs.

\BigGapNoBreak

\href{https://github.com/miloszkowal/seshat}
{\textbf{Seshat}} | Flask, Bootstrap, PostgreSQL, ElasticSearch, Heroku
\hfill

\GapNoBreak
Full-stack application that allows users to create personalized accounts and add books they have read. Provides statistics on book readership and stores all data in a PostgreSQL database.

% \href{http://commons.trincoll.edu/tcsp}
% {\textbf{Trinity College Student Photographers (TCSP)}},
% Trinity College
% \hfill
% \DatestampYMD{2015}{10}{01} --
% \DatestampYMD{2018}{01}{01}

% \GapNoBreak
% \BulletItem
% Founder, Chief Executive Officer
% \begin{detail}
% \SubBulletItem
% Employed 20 students, establishing TCSP as a premier employment opportunity for the Trinity community.
% \SubBulletItem
% Provided photography and event coverage services for over 70 events on campus, providing deliverables for each event within 24 hours.
% \SubBulletItem
% Managed social media accounts using Hootsuite, Mailchimp, and Later, with collective following of over 200.
% \end{detail}

\begin{comment}

%ABOUT TIME WITH TRIPOD

\href{http://commons.trincoll.edu/tripod}
{\textbf{Trinity Tripod}},
Trinity College
\hfill
\DatestampYMD{2017}{08}{01} --
\DatestampYMD{2018}{01}{01}

\GapNoBreak
\BulletItem
Photography Editor
\begin{detail}
\SubBulletItem
Collaborated with Trinity College Student Photographers to provide photographic content for weekly paper.
\SubBulletItem
Delivered hundreds of images for a variety of different stories, including custom stock imagery.
\SubBulletItem
Developed automated system for photo captioning using EXIF data, extracted using Adobe InDesign, resulting in 75\% time decrease when formatting images.
\end{detail}
\end{comment}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\noindent\hrulefill
\section
{Languages}
{Languages}
{PDF:Languages}

English (fluent), Polish (native), French (intermediate).

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Interests}
{Interests}
{PDF:Interests}

Editorial photography, works of Fyodor Dostoevsky, podcast production, applied mathematics.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\begin{comment}
\section
{References}
{References}
{PDF:References}

Available upon request.
\end{comment}
\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\begin{flushright}
\UseNoteFont
%[\textit{\CVNote}]
\hspace{2.0mm}\null
\end{flushright}
%\label{LastPage}
\end{document}
